Title here

### 2017-07-07 portfolio/text/ms.Rmd
2016 -> 2017 for permit prices

[^1]: For example, it cost ~\$192K USD for a king and tanner crab permit in
Southeast Alaska in 2016: <https://www.cfec.state.ak.us/pmtvalue/X_K69A.HTM>.

>>>>

[^1]: For example, it cost ~\$192K USD for a king and tanner crab permit in
Southeast Alaska in 2017: <https://www.cfec.state.ak.us/pmtvalue/X_K69A.HTM>.
